Outputs - civil servants' survey

### 2024-12-08 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

@@

```{r}
sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2)
```

>>>>

```{r}
#regression outputs with CIs
sjPlot::tab_model(politicization_mod1,influence_mod1,
                  show.std=T
)
```

@@

```{r}
#regression outputs with CIs
sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2,
                  show.std=T
)
```
